### 2022-07-21 doc/TrashData.tex
Changed Santek:Santek marginal costs so they equal the the calibrated marginal costs of other Santek products.

\caption{\label{tab:}Republic/Santek Merger Simulation Inputs}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrrrrr}
\toprule
Disposal Firm & Collection Firm & Volume (000s) & Disposal Price & Disposal Margin (\$) & Collection Margin (\$) & Collection Price\\
\midrule
Republic & Republic & 165 & 42 & 0 & 44 & 179\\
Santek & Republic & 34 & 36 & 20 &  & 174\\
Santek & Santek & 218 & 16 & 0 &  & 134\\
Santek & WM\_ADS & 30 & 36 & 20 &  & 221\\
Santek & Regional & 30 & 36 & 20 &  & 221\\
\addlinespace
WasteConn & Republic & 19 & 25 & 14 &  & 162\\
WasteConn & WasteConn & 48 & 11 & 0 &  & 110\\
WasteConn & WM\_ADS & 17 & 25 & 14 &  & 210\\
WasteConn & Regional & 17 & 25 & 14 &  & 210\\
\bottomrule
\end{tabular}}
\end{table}

>>>>

\caption{\label{tab:}Republic/Santek Merger Simulation Inputs}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrrrrr}
\toprule
Disposal Firm & Collection Firm & Volume (000s) & Disposal Price & Disposal Margin (\$) & Collection Margin (\$) & Collection Price\\
\midrule
Republic & Republic & 165 & 42 & 0 & 44 & 179\\
Santek & Republic & 34 & 36 & 20 &  & 173\\
Santek & Santek & 218 & 16 & 0 &  & 134\\
Santek & WM\_ADS & 30 & 36 & 20 &  & 221\\
Santek & Regional & 30 & 36 & 20 &  & 221\\
\addlinespace
WasteConn & Republic & 19 & 25 & 14 &  & 162\\
WasteConn & WasteConn & 48 & 11 & 0 &  & 110\\
WasteConn & WM\_ADS & 17 & 25 & 14 &  & 210\\
WasteConn & Regional & 17 & 25 & 14 &  & 210\\
\bottomrule
\end{tabular}}
\end{table}
